Tables

### 2020-11-11 tables.Rmd
not great

```{r, fig.width=3.5, fig.height=3}
ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University

@@

plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
```

>>>>

```{r, fig.width=3.5, fig.height=3}
#ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
ego_df <- readRDS('./assets/tables/table_ego_pubu.RDS')
univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University

@@

pdf(str_c('assets/figures/', "ego_network_figure.pdf"), paper = "a4r")
par(mfrow=c(2, 2))
plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))

dev.off()

```

```{r, fig.width=3.5, fig.height=3}
type_vec <- c("privu","pubu")
  #type_vec

for (i in 1:length(type_vec)) {

  #df_name <- str_c("table_ego_",type_vec[i],".RDS")
  ego_df <-readRDS(file.path('.','assets','tables',str_c("table_ego_",type_vec[i],".RDS")))
  #ego_df %>% glimpse() %>% print()

  univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University

  pdf(file.path('.','assets','figures',str_c("ego_network_figure_",type_vec[i],".pdf")), paper = "a4r")

  plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
  plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
  plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
  plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))

  dev.off()
}

```
